Essays in Computational Management Science

### 2018-05-10 Chapters/Chapter02.tex
refs.

@@

Sparse Distributed Memory (SDM) \citep{Kanerva1988} (see also \citep{kanerva_sparse_1993, denning_sparse_1989} is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model may be applied in all sort of applications because of its incredible ability to closely reflect the human capacity to remember past experiences from the subtlest of clues.

>>>>

from call admission control \citep{kwon_atm_1998, hee-yong_kwon_atm_1997}, to behavior-based robotics \citep{Rajesh1998, mendes2008robot, jockel_sparse_2009}, to noise filtering \citep{meng_modified_2009} and many others

There has recently been a surge of hardware implementations to minimize energy expenditure \citep{kang_energy-efficient_2015, kang_-memory_2016, li_hyperdimensional_2016, montagna_pulp-hd:_2018, salahuddin_energy_nodate}.

see the recent work on modern machine learning and reinforcement learning \citep{aguiar_sdm-go:_2013, wu_kanerva_2018}

@@

Sparse Distributed Memory (SDM) \citep{Kanerva1988} (see also \citep{denning_sparse_1989,  flynn_sparse_1989, kanerva_sparse_1993, kanerva_parallel_1985, goos_binary_1996, kanerva_hyperdimensional_2009,  keeler_comparison_1988, rwcp_fully_1997, marinaro_spatter_1994, sahlgren_permutations_nodate, uesaka_foundations_2001}) is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model is used in all sort of applications due to its incredible ability to closely reflect the human capacity to remember past experiences from the subtlest of clues. Applications range from call admission control \citep{kwon_atm_1998, hee-yong_kwon_atm_1997}, to behavior-based robotics \citep{Rajesh1998, mendes2008robot, jockel_sparse_2009}, to noise filtering \citep{meng_modified_2009}, etc.
